Thermodynamic characterization of the adsorption of amino acids onto pristine graphene and graphene oxide

### 2021-12-25 paper/main.tex

@@

\subsubsection{Well-Tempered Multiple Walker Metadynamics}

@@

>>>>

or, equivalently:

\begin{equation}
\label{eq:Aads-from-PMF-p}
\Delta A^{ads} = - k_B T \ln \left(\frac{\sum_{j \in near} p_{\xi_j}}{\sum_{k \in free} p_{\xi_k}}\right)
\end{equation}

@@

Umbrella sampling\cite{Torrie_1977} was used to obtain the PMF along
reaction coordinate by sampling multiple windows along $\xi$. Each sample
was obtained from a simulation where the Hamiltonian included the
following potential:

\begin{equation}
\label{eq:umbrella-potential}
\mathcal{V}^{US}(\mathbf{r}, k^{US}, \xi^0) = \frac{1}{2}k^{US}[\xi^0
- \xi(\mathbf{r})]^2
\end{equation}

where $\xi^0$ is the center of the sampling window and $k^{US}$ is an
harmonic constant. For simulations of amino acids over pristine
graphene $\xi^0$ took values from 0.3 to 1.5 nm in 0.05 nm steps, while $k^{US}$ took
values from 1000 to 12000 [$kJ \cdot mol \cdot nm^2$] adjusted to
ensure a good overlap in the sampling of different windows while
retaining a high sampling of the window's center.

The biased samples of $\xi$ obtained from these windows were used
to obtain the unbiased PMF using an implementation of the Weighted Histogram Analysis
Method (WHAM)\cite{Kumar_1992, Kumar_1995} developed by
\citet{WHAM}. This implementation of WHAM outputs --in addition to the
free energy/probability along $\xi$-- the (dimensionless) free energy
of each window, $F_i$. Knowing the $F_i$ of every we can unbias our
samples of any property $T$, to get an average for the window:

\begin{equation}
\label{eq:WHAM-unbias}
\langle T(\xi') \rangle = \frac{\sum_i^{S} \sum_j^{N_i} T_{i, j}
  e^{-\beta[F_i - \mathcal{V}^{US}(\mathbf{r_j})]}
  \delta \xi_{i, j}}{\sum_i^{S} \sum_j^{N_i}
  e^{-\beta[F_i - \mathcal{V}^{US}(\mathbf{r_j})]}
  \delta \xi_{i, j}}
\end{equation}

where

%\subsubsection{Well-Tempered Multiple Walker Metadynamics}

@@

Graphene sheets with sides of length $4.94$ and $4.87$ nm and
bond-length of $0.139$ nm were generated with VMD\cite{Humphrey_1996}
using its nanotube builder plugin.

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{/home/mbarria/Documents/Papers/graphene_adsorption_paper/figures/Graphene.png}}
\caption[]{\label{fig:system-pristine} Example of a simulated
  system. A Phenylalanine molecule is placed above a layer of pristine
  graphene inside a water-filled rectangular box. Carbon atoms are
  depicted in gray.}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{/home/mbarria/Documents/Papers/graphene_adsorption_paper/figures/Graphene_Oxide.png}}
\caption[]{\label{fig:system-oxide} (a) A simulated system where the
  graphene layer is oxidized. Carbon atoms are depicted in cyan, while
oxygen and hydrogen atoms are depicted in red and white,
respectively. (b) A section of the graphene oxide layer, showing the
distribution of the hydroxyl groups.}
\end{figure}
